---
title: "lin_reg"
author: "Alina Levine"
date: "December 9, 2018"
output: html_document
---


```{r}
library(tidyverse)
library(ggplot2)
library(HH)
library("leaps")
```



#data cleaning

I want to fit one model where I include cancer incidence rate and one where I don't 

pct other race does not make sense bc race percentages should add up to 100 but they do not. pct_some_col18_24 lin combo of 3 other variables

```{r}
  
  death_data_full = read_csv("data/Cancer_Registry.csv") %>%
    janitor::clean_names() %>%
    mutate(median_age = ifelse(median_age >60, NA, median_age)) %>%
    separate(geography, into = c("county", "state"), sep = ", ") %>%
    mutate(study_per_cap = ifelse(study_per_cap == 0,0,1)) %>%
    mutate(race_other = pct_other_race + pct_asian) %>%
    mutate(state = ifelse(state == "District of Columbia", "DC", state.abb[match(state, state.name)])) %>% 
    mutate(region_w = ifelse(state == "WA" | state == "MT" | state == "ID" | state == "OR" | state == "WY" | state == "NV" | state == "UT" | state == "CO" | state == "CA", 1, 0),
           region_sw = ifelse(state == "AZ" | state == "NM" | state == "TX" | state == "OK", 1, 0),
           region_me = ifelse(state == "ND" | state == "SD" | state == "NE" | state == "KS" | state == "MN" | state == "IA" | state == "MO" | state == "WI" | state == "IL" | state == "MI" | state == "IN" | state == "OH", 1, 0),
           region_se = ifelse(state == "AR" | state == "LA" | state == "MS" | state == "AL" | state == "GA" | state == "FL" | state == "SC" | state == "NC" | state == "TN" | state == "KY" | state == "VA" | state == "WV" | state == "MD" | state == "DC" , 1, 0))
    
  death_data = death_data_full %>%
    janitor::clean_names() %>%
    dplyr::select(-c(avg_ann_count,avg_deaths_per_year, pct_some_col18_24, binned_inc, county, pct_asian, pct_other_race,state))



```



#data cleaning

I want to fit one model where I include cancer incidence rate and one where I don't 

pct other race does not make sense bc race percentages should add up to 100 but they do not. pct_some_col18_24 lin combo of 3 other variables


#expoloratory plots

```{r}


ggplot(death_data_full, aes(x = target_death_rate)) +
  geom_histogram()

ggplot(data = death_data_full, aes( x= med_income, y = target_death_rate)) +
  geom_point()   #should I add a polynomial term for this


ggplot(data = death_data_full, aes( x= median_age, y = target_death_rate)) +
  geom_point()

#age does not look related unless there are confounders for age



ggplot(data = death_data_full, aes( x= median_age, y = target_death_rate)) +
  geom_point()


ggplot(data = death_data_full, aes( x= pct_black, y = target_death_rate)) +
  geom_point()


ggplot(data = death_data_full, aes( x= pct_white, y = target_death_rate)) +
  geom_point()


ggplot(data = death_data_full, aes( x= pct_unemployed16_over, y = target_death_rate)) +
  geom_point() 


ggplot(data = death_data_full, aes( x= pct_bach_deg18_24, y = target_death_rate)) +
  geom_point() 


```



median income and poverty_percent are highly correlated, so I will just use median income
percent private coverage and pct_public_coverage_alone are highly negatively correlated: because when more people have just public covergage, fewer people have private coverage

#Multicollinearity

```{r}
cor(death_data %>%select_if(is.numeric))
death_data_1 = death_data %>%
  dplyr::select(-c(med_income, pct_private_coverage))

fit_full_1 = lm(target_death_rate ~., data = death_data_1)

vif(fit_full_1)
#median_age_male, #median_age_female have high vif, I will take those out and just use median age
#percent_white and #percent_black have high vif, I will take out pct_black
#pct_married_households has high vif
#pct_employed16_over has high vif, pct_private_coverage_alone

death_data_2 = death_data_1 %>%
  dplyr::select(-c(pct_white, median_age_female, median_age_male, pct_married_households, pct_private_coverage_alone, pct_employed16_over))

fit_full_2 = lm(target_death_rate ~., data = death_data_2)

vif(fit_full_2)


#there is still high-multicollinearity among insurance variables, so I will remove 
#pct_public_coverage_alone


death_data_3 = death_data_2 %>%
  dplyr::select(-c(pct_public_coverage, pct_bach_deg25_over))
  

fit_full_3 = lm(target_death_rate ~., data = death_data_3)

vif(fit_full_3)

#will remove pct_private_coverage


```







#expoloratory plots

```{r}

ggplot(data = death_data_full, aes( x= med_income, y = target_death_rate)) +
  geom_point()   #should I add a polynomial term for this


ggplot(data = death_data_full, aes( x= median_age, y = target_death_rate)) +
  geom_point()

#age does not look related unless there are confounders for age



ggplot(data = death_data_full, aes( x= median_age, y = target_death_rate)) +
  geom_point()


ggplot(data = death_data_full, aes( x= pct_black, y = target_death_rate)) +
  geom_point()


ggplot(data = death_data_full, aes( x= pct_white, y = target_death_rate)) +
  geom_point()


ggplot(data = death_data_full, aes( x= pct_unemployed16_over, y = target_death_rate)) +
  geom_point() 


ggplot(data = death_data_full, aes( x= pct_bach_deg18_24, y = target_death_rate)) +
  geom_point() 


```



median income and poverty_percent are highly correlated, so I will just use median income
percent private coverage and pct_public_coverage_alone are highly negatively correlated: because when more people have just public covergage, fewer people have private coverage

#Multicollinearity

#Stepwise

```{r}
model = fit_full_4

step(fit_full_3, direction='backward')


model_stepwise = lm(formula = target_death_rate ~ poverty_percent + median_age + 
    avg_household_size + percent_married + pct_no_hs18_24 + pct_hs18_24 + 
    pct_bach_deg18_24 + pct_hs25_over + pct_unemployed16_over + 
    pct_emp_priv_coverage + pct_public_coverage_alone + pct_black + 
    birth_rate + race_other + region_w + region_se + incidence_rate, data = death_data_3)

summary(model_stepwise)


```
variables selected are : incidence rate, pop_est2015, poverty_percent, pct_no_hs18_24, pct_hs18_24, pct_bach_deg25_over, pct_unemployed16_over, pct_emp_priv_coverage, pct_public_coverage, pct_white, birth_rate


#Criteria

```{r}




best <- function(model, ...) 
{
  subsets <- regsubsets(formula(model), model.frame(model), ...)
  subsets <- with(summary(subsets),
                  cbind(p = as.numeric(rownames(which)), which, rss, rsq, adjr2, cp, bic))
  
  return(subsets)
}  

View(best(fit_full_3))
```

the cp is minimized and adjusted r squared is maximimized in the following model:

incidence rate, poverty_percent, pct_nohs_18_24, pct_hs_18_24, pct_bachdeg_25_over, pct_unemployed16_over, pct_emp_priv_coverage_ birth_rate 
