---
title: "Untitled"
author: "haokun yuan"
date: "12/14/2018"
output: html_document
---


```{r}
library(tidyverse)
library(ggplot2)
library(HH)
library("leaps")
library(caret)
```



#data cleaning

I want to fit one model where I include cancer incidence rate and one where I don't 

pct other race does not make sense bc race percentages should add up to 100 but they do not. pct_some_col18_24 lin combo of 3 other variables

```{r}
  
death_data_full = read_csv("data/Cancer_Registry.csv") %>%
    janitor::clean_names() %>%
    mutate(median_age = ifelse(median_age >60, NA, median_age)) %>%
    separate(geography, into = c("county", "state"), sep = ", ") %>%
    mutate(study_per_cap = ifelse(study_per_cap == 0,0,1)) %>%
    mutate(race_other = pct_other_race + pct_asian) %>%
    mutate(state = ifelse(state == "District of Columbia", "DC", state.abb[match(state, state.name)])) %>% 
    mutate(region_w = ifelse(state == "WA" | state == "MT" | state == "ID" | state == "OR" | state == "WY" | state == "NV" | state == "UT" | state == "CO" | state == "CA", 1, 0),
           region_sw = ifelse(state == "AZ" | state == "NM" | state == "TX" | state == "OK", 1, 0),
           region_me = ifelse(state == "ND" | state == "SD" | state == "NE" | state == "KS" | state == "MN" | state == "IA" | state == "MO" | state == "WI" | state == "IL" | state == "MI" | state == "IN" | state == "OH", 1, 0),
           region_se = ifelse(state == "AR" | state == "LA" | state == "MS" | state == "AL" | state == "GA" | state == "FL" | state == "SC" | state == "NC" | state == "TN" | state == "KY" | state == "VA" | state == "WV" | state == "MD" | state == "DC" , 1, 0)) %>% 
   unite(geography,c(county, state), sep = ", ")
    

sex_data = read_csv("./data/SEX01.csv") %>% 
  dplyr::select(Areaname,SEX255209D) %>% 
  separate(Areaname, c("county","state"), sep = ", ") %>% 
  na.omit() %>% 
  mutate(county = paste(county,"County", sep = " "),
         sex_ratio = SEX255209D) %>% 
  unite(geography,c(county, state), sep = ", ") %>% 
  dplyr::select(geography,sex_ratio)

age_data=read_csv("./data/AGE04.csv") %>% 
  dplyr::select(Areaname,AGE775208D) %>% 
  separate(Areaname, c("county","state"), sep = ", ") %>% 
  na.omit() %>% 
  mutate(county = paste(county,"County", sep = " "),
         pct_aging = AGE775208D) %>% 
  unite(geography,c(county, state), sep = ", ") %>% 
  dplyr::select(geography,pct_aging)

cancer_1 = left_join(death_data_full,sex_data,by = "geography")
death_data_full = left_join(cancer_1,age_data,by = "geography") 

death_data_full = death_data_full %>% 
  separate(geography, c("county","state"), sep = ", ")

death_data =
  death_data_full %>%
  janitor::clean_names() %>%
  dplyr::select(-c(avg_ann_count,avg_deaths_per_year, pct_some_col18_24, binned_inc, county, pct_asian, pct_other_race,state)) %>% 
  mutate(sex_ratio = replace_na(sex_ratio,50.2), pct_aging = replace_na(pct_aging,15.58), pct_private_coverage_alone = replace_na(pct_private_coverage_alone,48.48), pct_employed16_over = replace_na(pct_employed16_over,48.48), median_age = replace_na(median_age,40.82))
                                                                                                                                    
                                                                    
```



#data cleaning

I want to fit one model where I include cancer incidence rate and one where I don't 

pct other race does not make sense bc race percentages should add up to 100 but they do not. pct_some_col18_24 lin combo of 3 other variables


#expoloratory plots

```{r}


ggplot(death_data_full, aes(x = target_death_rate)) +
  geom_histogram()

ggplot(data = death_data_full, aes( x= med_income, y = target_death_rate)) +
  geom_point()   #should I add a polynomial term for this


ggplot(data = death_data_full, aes( x= median_age, y = target_death_rate)) +
  geom_point()

#age does not look related unless there are confounders for age



ggplot(data = death_data_full, aes( x= median_age, y = target_death_rate)) +
  geom_point()


ggplot(data = death_data_full, aes( x= pct_black, y = target_death_rate)) +
  geom_point()


ggplot(data = death_data_full, aes( x= pct_white, y = target_death_rate)) +
  geom_point()


ggplot(data = death_data_full, aes( x= pct_unemployed16_over, y = target_death_rate)) +
  geom_point() 


ggplot(data = death_data_full, aes( x= pct_bach_deg18_24, y = target_death_rate)) +
  geom_point() 


```



median income and poverty_percent are highly correlated, so I will just use median income
percent private coverage and pct_public_coverage_alone are highly negatively correlated: because when more people have just public covergage, fewer people have private coverage

#Multicollinearity

```{r}
cor(death_data %>%select_if(is.numeric))
death_data_1 = death_data %>%
  dplyr::select(-c(med_income, pct_private_coverage))

fit_full_1 = lm(target_death_rate ~., data = death_data_1)

vif(fit_full_1)

## Delete varibles with high vif
death_data_2 = death_data_1 %>%
  dplyr::select(-c(pct_white, median_age, percent_married, pct_public_coverage, median_age_male))

fit_full_2 = lm(target_death_rate ~., data = death_data_2)

vif(fit_full_2)



## Delete variables with vif > 5, keep poverty_percent since it provided more information
death_data_3 = death_data_2 %>%
  dplyr::select(-c(pct_emp_priv_coverage, pct_bach_deg25_over ))
  

fit_full_3 = lm(target_death_rate ~., data = death_data_3)

vif(fit_full_3)

summary(fit_full_3)


```







#expoloratory plots

```{r}

ggplot(data = death_data_full, aes( x= med_income, y = target_death_rate)) +
  geom_point()   #should I add a polynomial term for this


ggplot(data = death_data_full, aes( x= median_age, y = target_death_rate)) +
  geom_point()

#age does not look related unless there are confounders for age



ggplot(data = death_data_full, aes( x= median_age, y = target_death_rate)) +
  geom_point()


ggplot(data = death_data_full, aes( x= pct_black, y = target_death_rate)) +
  geom_point()


ggplot(data = death_data_full, aes( x= pct_white, y = target_death_rate)) +
  geom_point()


ggplot(data = death_data_full, aes( x= pct_unemployed16_over, y = target_death_rate)) +
  geom_point() 


ggplot(data = death_data_full, aes( x= pct_bach_deg18_24, y = target_death_rate)) +
  geom_point() 


```



median income and poverty_percent are highly correlated, so I will just use median income
percent private coverage and pct_public_coverage_alone are highly negatively correlated: because when more people have just public covergage, fewer people have private coverage

#Multicollinearity


#Criteria

```{r}
best <- function(model, ...) 
{
  subsets <- regsubsets(formula(model), model.frame(model),nvmax = NULL, ...)
  subsets <- with(summary(subsets),
                  cbind(p = as.numeric(rownames(which)), which, rss, rsq, adjr2, cp, bic))
  
  return(subsets)
}  

knitr::kable(best(fit_full_3))

View(best(fit_full_3)[18,]) #use model from row 18 cp is 18.3
```

```{r}
reg_cp = lm(target_death_rate ~ incidence_rate + study_per_cap + median_age_female + 
           pct_hs18_24 + pct_bach_deg18_24 + 
           pct_hs25_over + pct_employed16_over + pct_unemployed16_over + 
           pct_public_coverage_alone + pct_black + 
           pct_married_households + birth_rate + race_other + region_w + region_sw + 
           region_me + region_se + sex_ratio + pct_aging, data = death_data_3)

summary(reg_cp)
```

identify outlier

```{r}
stu_res = rstandard(reg)

outliers_y = stu_res[abs(stu_res) > 2.5]
outliers_y

brand.hat = hatvalues(reg)
brand.hat[brand.hat > 0.2]
brand.hat[brand.hat > 2*17/3059]
hist(brand.hat)
influence.measures(reg)
```

Diagnostic Plot

```{r}
plot(reg)
```

Cross Validation

```{r}
set.seed(1)
data_train = trainControl(method = "cv", number = 10)
model_caret = train(target_death_rate ~ incidence_rate + poverty_percent
                    + avg_household_size + percent_married + pct_hs18_24
                    + pct_bach_deg18_24 + pct_hs25_over +
                      pct_unemployed16_over + pct_public_coverage_alone +
                      pct_black + birth_rate + race_other + region_w +
                      region_sw + region_me +
                      region_se + sex_ratio + pct_aging, data =
                      death_data_3,
                    trControl = data_train,
                    method = 'lm',
                    na.action = na.pass)
model_caret
model_caret$finalModel
```

```{r}

```

